%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LaTeX Template: Curriculum Vitae
%
% Source: http://www.howtotex.com/
% Feel free to distribute this template, but please keep the
% referal to HowToTeX.com.
% Date: July 2011
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% How to use writeLaTeX: 
%
% You edit the source code here on the left, and the preview on the
% right shows you the result within a few seconds.
%
% Bookmark this page and share the URL with your co-authors. They can
% edit at the same time!
%
% You can upload figures, bibliographies, custom classes and
% styles using the files menu.
%
% If you're new to LaTeX, the wikibook is a great place to start:
% http://en.wikibooks.org/wiki/LaTeX
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[paper=a4,fontsize=11pt]{scrartcl} % KOMA-article class
							
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath,amsfonts,amsthm}     % Math packages
\usepackage{graphicx}                    % Enable pdflatex
\usepackage[svgnames]{xcolor}            % Colors by their 'svgnames'
\usepackage{geometry}
	\textheight=700px                    % Saving trees ;-)
\usepackage{tcolorbox}
\usepackage{multicol}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{tabularx}
% \usepackage{showframe}

\frenchspacing              % Better looking spacings after periods
\pagestyle{empty}           % No pagenumbers/headers/footers

%%% Custom font
%%% ------------------------------------------------------------
\usepackage[sfdefault]{cabin}
\usepackage[T1]{fontenc}

%%% Custom sectioning (sectsty package)
%%% ------------------------------------------------------------
\usepackage{sectsty}

\sectionfont{%			            % Change font of \section command
	\usefont{OT1}{phv}{b}{n}%		% bch-b-n: CharterBT-Bold font
	\sectionrule{0pt}{0pt}{-5pt}{3pt}}

%%% Colors
%%% ------------------------------------------------------------
% https://coolors.co/fdfffc-235789-c1292e-f1d302-161925
\definecolor{yel}{HTML}{F1D302}
\definecolor{red}{HTML}{C1292E}
\definecolor{blu}{HTML}{235789}
\definecolor{blk}{HTML}{161925}
\hypersetup{colorlinks=true,urlcolor=red}

\makeatletter
\newcommand{\globalcolor}[1]{%
  \color{#1}\global\let\default@color\current@color
}
\makeatother

\AtBeginDocument{\globalcolor{blk}}

\newtcolorbox{bigredbox}[1][]{
  enhanced,
  arc=0pt,
  outer arc=0pt,
  colback=red,
  boxrule=0.8pt,
  #1
}

%%% Macros
%%% ------------------------------------------------------------
\newlength{\spacebox}
\settowidth{\spacebox}{8888888888}			% Box to align text
\newcommand{\sepspace}{\vspace*{1em}}		% Vertical space macro
\newcommand{\sym}{\raisebox{1pt}{$\blacktriangleright$}}
\newcommand{\showurl}[1]{\href{#1}{#1}}

\newcommand{\MyName}[5]{ % Name
	\setlength\parskip{0cm}
	\noindent
	\begin{minipage}[c]{ 4.1cm }
		\begin{tcolorbox}[colback=yel,colframe=yel,halign title=left,boxsep=0mm,left=2mm,flush left]
			\color{blk}
			\fontsize{90pt}{90pt}\selectfont \usefont{OT1}{phv}{b}{n} cv
		\end{tcolorbox}
	\end{minipage}
	\begin{minipage}[t]{ 10.6cm }
		\vspace{-3.2em}
		\hfill \huge \usefont{OT1}{phv}{b}{n} #1
		\par \hfill \large \usefont{OT1}{phv}{m}{n} \textit{#2} % Subtitle
		\par \hfill \small \usefont{OT1}{phv}{m}{n} \textit{#3} % Address line 1
		\par \hfill \small \usefont{OT1}{phv}{m}{n} \textit{#4} % Address line 2
		\par \hfill \small \usefont{OT1}{phv}{m}{n} \textit{#5} % Address line 3
	\end{minipage}
	\par \normalsize \normalfont
}

\newcommand{\NewPart}[1]{\section*{\sym \mbox{} \MakeUppercase{#1}}}

\newcommand{\PersonalEntry}[2]{
		\noindent\hangindent=2em\hangafter=0 % Indentation
		\parbox{\spacebox}{        % Box to align text
		\textit{#1}}		       % Entry name (birth, address, etc.)
		\hspace{1.5em} #2 \par
		\sepspace}

\newcommand{\SkillsEntry}[2]{      % Same as \PersonalEntry
		\noindent
		\begin{tabularx}{\linewidth}{ p{7em} X }
			\noindent
			\begin{minipage}[t]{7em}
				\textbf{#1}
			\end{minipage} &
			\noindent \normalfont \small #2
		\end{tabularx}
		\sepspace}
		
\newcommand{\EducationEntry}[5]{
		\Large \noindent \textbf{#1} \hfill \\   % Degree
		\normalsize \noindent \textit{#2} \hfill	  % School
		\colorbox{yel}{\color{blk}#3} \par  % Duration
		\noindent \textit{#4} \par        % School
		\noindent\hangindent=2em\hangafter=0 \small #5 % Description
		\normalsize \par
		\sepspace}

\newcommand{\WorkEntry}[4]{				  % Same as \EducationEntry
		\noindent \textbf{#1} \hfill      % Jobname
		\colorbox{yel}{\color{blk}#2} \par  % Duration
		\noindent \textit{#3} \par              % Company
		\noindent\hangindent=2em\hangafter=0 \small #4 % Description
		\normalsize \par
		\sepspace}

%%% ------------------------------------------------------------
%%% BEGIN DOCUMENT
%%% ------------------------------------------------------------

\begin{document}

\MyName{BENJAMIN MASTRIPOLITO}{benpm@cs.utah.edu}{1304 E 900 S Apt 2}{Salt Lake City, UT 84105}{USA}

\sepspace


%%% Education
%%% ------------------------------------------------------------
\NewPart{Education}{}

\EducationEntry{University of Utah}{University of Utah}{August 2024}{Advisor: Dr. Cem Yuksel, 3.9 GPA}

\EducationEntry{Bachelors of Science in Computer Science}{New Mexico Institute of Mining and Technology (NMT)}{May 2020}{3.79 GPA}



%%% Work experience
%%% ------------------------------------------------------------
\NewPart{Work Experience}{}

\WorkEntry{Research Assistant}
{Fall 2023 - May 2024}{University of Utah}{\noindent
	\begin{itemize}
		\item Research assistant under Dr. Cem Yuksel (\textit{cem@cemyuksel.com}) working on polygon-agnostic 3D modeling research in OpenGL and C++
	\end{itemize}
}

\WorkEntry{Post-Baccalaureate Student}
{June 2020 - July 2022}{Los Alamos National Laboratory}{\noindent
	\begin{itemize}
		\item Research on parallel interpolation algorithms for physical equation-of-state data
		      under mentorship of Dr. Daniel Sheppard (\textit{danielsheppard@lanl.gov})
		\item Developed Python plotting package for physical equation-of-state data
	\end{itemize}
}

\WorkEntry{Parallel Computing Summer Research Internship}
{June 2019 - Aug 2019}{Los Alamos National Laboratory}{\noindent
	\begin{itemize}
		\item Worked as a student in the Parallel Computing Summer Research Internship at LANL researching performance analysis techniques on parallel algorithms, under mentorship of Dr. Rao Garimella (\textit{rao@lanl.gov})
	\end{itemize}
}

\WorkEntry{Research Assistant}
{Jan 2019}{New Mexico Institute of Mining and Technology}{\noindent
	\begin{itemize}
		\item Worked with Dr. Denis Cohen (\textit{denis.cohen@gmail.com}) in developing a parallel, unstructured-mesh-based program for simulation of landslides using C++ and OpenMP
	\end{itemize}
}

% \WorkEntry{Student Worker - Mechanical Engineering Department}
% 	{Aug 2018 - Mar 2019}{New Mexico Institute of Mining and Technology}{\noindent
% 	\begin{itemize}
% 		\item Worked with Dr. Ashok Ghosh (ashok.ghosh@nmt.edu) on contract work to develop a web-based monitoring
% 			system for sea vessels.
% 	\end{itemize}
% }

% \WorkEntry{Student Worker - ITC}
% 	{May 2018 - Aug 2018}{New Mexico Institute of Mining and Technology}{\noindent
% 	\begin{itemize}
% 		\item Performed duties for the Information Technology and Communications department (ITC)
% 			involving maintenance of IT infrastructure on campus at NMT.
% 	\end{itemize}
% }


%%% Publications
%%% ------------------------------------------------------------
\NewPart{Publications}{}

\WorkEntry{\href{https://asmedigitalcollection.asme.org/computingengineering/article-abstract/22/2/021009/1121736/simd-Optimized-Search-Over-Sorted-Data}{SIMD-Optimized Search Over Sorted Data}}
{November 2021}{Los Alamos National Laboratory}


% p

\pagebreak

%%% Projects
%%% ------------------------------------------------------------
\NewPart{Portfolio}{}

\WorkEntry{Petting Zoo}{Ongoing}{\showurl{https://github.com/TheFutureGadgetsLab/PettingZoo}}{
	Machine learning environment with procedurally generated platformer levels.
	Supports training various types of neural networks with genetic algorithms.
}

\WorkEntry{Petri}{Ongoing}{\showurl{https://github.com/TheFutureGadgetsLab/Petri}}{
	High performance parallel particle simulator and renderer written in Rust with WebGPU backend.
}

\WorkEntry{Cellarium}{Ongoing}{\showurl{https://github.com/benpm/cellarium}}{
	WebGL cellular automata simulator which allows random generation of novel multi-state rules.
	Simulation is written in an optimized GLSL fragment shader, allowing for large simulations.
	Web app UI built with Vue.
}

\WorkEntry{CUDA / OpenGL Raytracer}{2020}{\showurl{https://github.com/benpm/cuda-raytracer}}{
	Created a parallel raytracing program using NVIDIA CUDA C++ and OpenGL.
	Supports refractive materials, diffuse lighting, antialiasing, and emissive materials.
}

\WorkEntry{LD48 Recursive Puzzle Game}{2021}{\showurl{https://github.com/benpm/ldjam48}}{
	Puzzle game where the level structure is manipulated through interactive objects,
	allowing for levels which contain themselves.
	Made in 72 hours for the 48th Ludum Dare game jam, where it won 2nd place in the Innovation category
	out of almost 4000 submissions.
}



%%% Skills
%%% ------------------------------------------------------------
\NewPart{Skills}{}

\SkillsEntry{C / C++}{
	Extensive experience working in the C and C++ programming languages in both academic and professional settings.
}

\SkillsEntry{Graphics APIs}{
	Experience with creating complex applications OpenGL, WebGL, WebGPU, CUDA, DirectX 12. Working knowledge of Linear Algebra in the context of computer graphics.
}

\SkillsEntry{Interpersonal}{
	Multiple years of experience working directly with students tutoring mathematics and computer science. Experience working in a professional context with a moderate sized team of software engineers.
}

\SkillsEntry{Machine\\Learning}{
	Experience with machine learning techniques and frameworks such as PyTorch, TensorFlow, and Keras.
}

\SkillsEntry{Parallel\\Computing}{
	Experience with parallel computing techniques and frameworks such as OpenMP, MPI, and CUDA on very large compute clusters at Los Alamos National Laboratory.
}

\end{document}
